Modeling potential JCPOA diversion scenarios with Cyclus

### 2018-05-16 paper.tex
including Pat comments

Fuel cycle simulations, as any simulation process, do not produce results
without errors.  Those errors have different sources: data uncertainties (when
the simulation relies on previously estimated/measured metrics), modeling
uncertainties (produced by the simplification made by the simulator) and the
``operational`` uncertainty (uncertainty on the operation parameters of the
different facilities).

@@

To estimate the uncertainty on fuel cycle output metrics, a Total Monte
Carlo approach has been applied.  In the following, output metric uncertainty
corresponds to the Standard Deviation of the output metrics over about 200
different simulations.  For each deployed facilities, the uncertainty associated
parameters have been a normally distributed with an artificially large standard
deviation of $10\%$.

To pursuit this work, both the Cycamore\cite{cycamore} package\footnote{Low
fidelity facilities package for Cyclus} and the
CyCLASS\footnote{Reactor and Fuel fabrication facility based on
    CLASS\cite{CLASS}  models} have been
updated\cite{mouginot_2018, cyclass} to deal with uncertainty in several
operational parameters of their associated facilities.  Table
\ref{tab:package_uncertainty} summarizes all modification implemented in the
range of facilities present in Cycamore and CyCLASS.

@@

The uncertainty on the different parameters have been considered for this study
as systematic for each new deployed facilities: each time a new facility is
deployed (such as a reactor or a fuel fabrication facility) a new set a
parameter is computed.

\subsection{The Fuel Cycle}
This work aims to assess the impact of the operational uncertainties of a simple
transition as shown in Figure \ref{fig:cycle}, inspired from the EG23 fuel cycle
of the Nuclear Fuel Cycle Evaluation and Screening Report\cite{ES}: a
transition from light water reactors fleet loaded with \glspl{UOX} fuel to a
sodium fast reactor fleet loaded \glspl{MOX} fuel, considering an $1\%/$y growth
of the generated power (Figure \ref{fig:power}).
\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.31]{cycle.png}
  \caption{Illustration of the material flow between the different facilities,
  with in green each operational parameters associated with an
  uncertainty.}\label{fig:cycle}
\end{figure}

@@

In this works, a time step of 1 month have been considered, i.e. each output
metrics are reported one each month and decay process have not be taking into
account.

@@

For this study 6 set of 199 simulations, and a reference calculation have been
computed: One for each of the 5 uncertain parameters, one varying parameter the
4 others remaining fix, one with all 5 parameters varying and one single
simulation where all the 5 parameters were fixed at the mean value.

In the following, each total uncertainty is reported at $\pm1\sigma$ around the
mean values of the corresponding uncertainty set at each time step. The time
dependant relative uncertainty are computed as the standard deviation of a
single set over its mean value at the corresponding time.

@@

Indeed the transition scenario has been design to allow all the reactors to
receive the fuel as needed allowing them to be producing power all the time.
This ensures that the uncertainty measured any other parameters is not
influenced by the reactors miss-loadings.

%%  \begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
%%    \centering
%%    \includegraphics[scale=0.37]{power_uncer}
%%    \caption{}\label{fig:power_uncer}
%%  \end{figure}

@@

The fluctuation of the full relative uncertainty at low time are induced by the
fuel loading: all reactors at the beginning of the simulation have synchronised
cycle, this phenomenon disappears with the gradual decommissioning of the
initial reactors, spread on 50 years.

@@

With the increase of deployed reactors, the number of batches of \glspl{LWR}
fuel loaded converges to the references one (a random cycle length
values if randomly determined for each deployed reactors), reducing its impact
on the uncertainty on the total uranium consumption.
The fuel enrichment contribution follow a close to constant uncertainty
contribution of $2\%$, so as the total relative uncertainty decrease, its
relative contribution increases over time.

@@

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.18]{used_fuel}
    \caption{Used fuel inventory.}\label{fig:used_fuel}
\end{figure}
Between year 90 and 120, the \glspl{FBR} deployment speed increases, it has to
compensate the non replacement of the decommissioned \glspl{LWR} as well as
follow the power demand.  During this period the needs in plutonium are higher
than its productions, explaining the observed decrease of the total amount, and
the increase associated relative uncertainty.

@@

>>>>

Fuel cycle simulations, as any simulation process, do not produce results
without errors.  Those errors have different sources: data uncertainties (when
the simulation relies on previously estimated/measured metrics), modeling
uncertainties (produced by the simplifications made by the simulator) and the
``operational`` uncertainty (uncertainty on the operation parameters of the
different facilities).

@@

To estimate the uncertainty on fuel cycle output metrics, a Total Monte
Carlo approach has been applied.  In the following, output metric uncertainty
corresponds to the standard deviation of the output metrics 199
different simulations.  For each deployed facilities, the uncertainty associated
parameters have been a normally distributed with an artificially large standard
deviation of $10\%$.

To pursue this work, both the Cycamore\cite{cycamore} package\footnote{Low
fidelity facilities package for Cyclus} and the CyCLASS\footnote{Reactor and
Fuel fabrication facility based on CLASS\cite{CLASS}  models} have been
updated\cite{mouginot_2018, cyclass} to deal with uncertainty in several
operational parameters of their associated facilities.  Table
\ref{tab:package_uncertainty} summarizes all modification implemented in the
range of facilities present in Cycamore and CyCLASS.

@@

The uncertainty on the different parameters have been considered for this study
as systematic for each new deployed facilities: each time a new facility is
deployed (such as a reactor or a fuel fabrication facility) a new set of
parameter is computed.

\subsection{The Fuel Cycle Scenario}
This work aims to assess the impact of the operational uncertainties of a simple
transition as shown in Figure \ref{fig:cycle}, inspired from the EG23 fuel cycle
of the Nuclear Fuel Cycle Evaluation and Screening Report\cite{ES}: a
transition from light water reactors fleet loaded with \glspl{UOX} fuel to a
sodium fast reactor fleet loaded \glspl{MOX} fuel, considering an $1\%/$y growth
of the generated power (Figure \ref{fig:power}).
\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.31]{cycle.png}
  \caption{Illustration of the material flow between the different facilities,
  with in green each operational parameters associated with an
  uncertainty.}\label{fig:cycle}
\end{figure}

@@

In this work, a time step of 1 month have been considered, i.e.  each output
metrics are reported one each month and decay process have not be taking into
account.

@@

For this study 6 set of 199 simulations, and a reference calculation have been
computed: One for each of the 5 uncertain parameters,Tab.
\ref{tab:package_uncertainty}  (separation efficiency, residence time, UOX fuel
enrichment, reactor cycle length, reactor thermal power), one varying parameter
the 4 others remaining fix, one with all 5 parameters varying and one single
simulation where all the 5 parameters were fixed at the mean value.

In the following, each total uncertainty is reported at $\pm1\sigma$ around the
mean values of the corresponding uncertainty set at each time step.  The time
dependant relative uncertainties are computed as the standard deviation of a
single set over its mean value at the corresponding time.

@@

Indeed the transition scenario has been designed to allow all the reactors to
receive the fuel as needed allowing them to be producing power all the time.
This ensures that the uncertainty measured any other parameters is not
influenced by the reactors miss-loadings.  As \glspl{FBR} fuel is built from
reprocessed used fuels, the availability of those used fuels may impact the
capability to build the required MOX-FBR fuel.  Having reactor miss-loads, may
impact more miss-loading later during a simulation and lead to a snow-ball
effect.  Having a small uncertainty on the power generation ensures large miss
load effects are not to be considered here.

@@

@@

Uncertainty fluctuation of the full relative uncertainty can be observed before
year 50.  Those fluctuation are induced by the fuel loading: all reactors at the
beginning of the simulation have synchronised cycle, this phenomenon disappears
with the gradual decommissioning of the initial reactors, spread on 50 years.

The decrease of the cycle time uncertainty contribution, from year 30 to year
90, can be understand as an averaging effect.  As the uncertainty are considered
as systematic per deployed facility, each reactor will have a different cycle
length value, so a different number of loaded batches per year.With the increase
of deployed reactors, the number of batches of \glspl{LWR} fuel loaded converges
to the references one, reducing its impact on the uncertainty on the total
uranium consumption.

The fuel enrichment contribution follow a close to constant uncertainty
contribution of $2\%$, so as the total relative uncertainty decrease, its
relative contribution increases over time.

@@

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.18]{used_fuel}
    \caption{Used fuel inventory, corresponding to the amount of used
    \glspl{LWR} and \glspl{FBR} fuel, cooled and waiting to be reprocessed.}
    \label{fig:used_fuel}
\end{figure}
Between year 90 and 120, the \glspl{FBR} deployment speed increases, it has to
compensate the non replacement of the decommissioned \glspl{LWR} as well as
follow the power demand.  During this period the needs in plutonium are higher
than its productions, explaining the observed decrease of the total amount, and
the increase associated relative uncertainty.

@@

This preliminary study may suggest that the most important contribution to
natural uranium consumption and fissile inventory is coming from the time when
occurs the different material exchange between facilities, and not necessary
from the physical parameters such as thermal power or fuel enrichment. Further
analysis should allow us to confirm or denies it.
